Survey of Misuses of the Kolmogorov–Smirnov-Test

### 2022-03-04 Manuscript/manuscript.tex
added copula histogram and babu into fitted parameters histogram, removed block bs

To resolve this problem, parametric bootstrap can be performed. The parameters of the null distribution are approximated from the bootstrap. Figure~\ref{fig:hist_parametric} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$. In each parametric test, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated. In the naive case, K-S tests are performed with fitted parameters.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_parametric}
  \caption{Histograms demonstrating fitted parameters.}
  \label{fig:hist_parametric}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_block}
  \caption{Histograms of P-values when using block bootstrap.}
  \label{fig:hist_block}
\end{figure}

>>>>

To resolve this problem, parametric bootstrap can be performed. The parameters of the null distribution are approximated from the bootstrap. Figure~\ref{fig:hist_fitted} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$. In each parametric test, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated. In the naive case, K-S tests are performed with fitted parameters.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_fitted}
  \caption{Histograms demonstrating fitted parameters.}
  \label{fig:hist_fitted}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula}
  \caption{Histograms demonstrating copula to correct correlation.}
  \label{fig:hist_copula}
\end{figure}
